Joint Training of Classification and Similarity Models for \\ Intention Detection in Task-specific Chatbot

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
Reorganized.   modified:   paper.tex
  new file:   abstract.tex
  new file:   introduction.tex
  new file:   related_work.tex
  new file:   methodology.tex
  new file:   experiments.tex
  new file:   conclusion.tex

  \begin{abstract}
    Task-specific  chatbot systems have gained many important applications, such
    as  Siri,  Google home, and customer service systems, etc. One essential technique 
    underlying these applications  is to detect the real intention behind a user's input.
    The intention detection,  assuming  only  one  intention  in  a  user's input here, can be
    regarded  as  a  short  text  classification problem.  In  practice,  the  number  of
    intentions  can  be hundreds of thousands, as opposed to a few number in the
    traditional text classification problem; creating enough training data from tons of 
    raw user logs with miscellaneous information is not trivial, 
    and generally only 10 to 20 samples per intention are available in  the  early  stage.  
    Thus,  how  to  train  an  effective short-text classification model with
    limited labeled data  in such a practical  and important application is critical. In this work, we propose a
    novel  model, called similarity model fused with classification model (SFC),
    which  combines  a  classification  model  and  a similarity model, and also
    borrows  the  power  of  multi-task  training  as well. We conduct extensive
    experiments  on  4  public  and 1 private datasets. Experimental results
    show that our new model outperforms very strong baselines (i.e., BERT, RoBERTa and
    ALBERT based pretrained models) by over 2 percentages in average F1 score.

  \end{abstract}

  \section{Introduction}
  \label{sec:intro}

  Task-specific  conversational  chatbot  \cite{wen2016network}  has been applied
  into  many practical products. One typical example is the chatbot that shares the working burden of
  human  customer  service  agents  responsible  for  customers' questions about
  certain  products  or services. Another one is the speech-based control in
  devices  like  intelligent  speakers, such as Siri, Google home, Baidu Xiaodu,
  and smart home equipments, to name a few. Regardless of whether these conversations belong to
  single or  multi-round, an essential technique underlying this type of chatbot is to
  identify  the  real  intention  behind  a  user's  question or reply. 
  The detected intention  with  its  associated  information  is then mapped into a
  predefined dialog logic graph, from which a suitable response (e.g., conducting 
  expected actions, replying texts or accomplishing some operations, etc)  is returned.
  This  is  the  main  difference  from  a  free chatbot.

  Intention detection in task-specific chatbot  is  a  challenging task due to some inherent properties. First,
  a customer's  utterance  within  a conversation is usually quite short. Since it
  does  not  contain  enough  information,  short  texts \cite{song2014short} are
  thought  to  be  more  ambiguous  compared to long texts such as paragraphs or
  documents,  posing  a  great challenge \cite{chen2019deep} for classification
  task   \cite{phan2008learning,yan2009dynamic,hua2015short}.   Second,  in  the
  initial  stage  of  building  a  chatbot  , it is often rather hard to collect
  sufficient  labeled  data  to  train  a good model. Because developers have to
  examine tons of real system logs for typical user's utterances, and then label
  them  with expected intentions. Therefore, to build a task-specific chatbot with
  high  performance, it is essential to solve the challenge of short-text
  classification   \cite{sriram2010short}   problem   under   few-shot   setting
  \cite{yu2018diverse}.

  Generally  there  are  two  kinds  of  approaches  to  address  this  problem,
  one is the classification model that directly maps an input into a most likely label, and
  the other one is the similarity  model  that searches a label whose associated data is most similar to
  an input.

  The   first  one,  \emph{text  classification},  includes  classic  long  text
  classification  and  short  text  classification  in  this  scenario.  Besides
  traditional  machine  learning  models  like  SVM \cite{suykens1999least},  
  boosting  tree \cite{tu2005probabilistic},  many work
  \cite{wen2016network}  choose  neural  network  such  as  convolutional neural
  networks (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very}
  and       long       short       term       memory       networks      (LSTMs)
  \cite{mousa2017contextual,liu2016recurrent}   to   accomplish   the   task  of
  extracting  semantic  feature from limited amount of words. Their common model
  structure  is  adding  a  softmax classifier as the final layer and mapping to
  labels.  Another  two  interesting lines of work, label-word joint models, and
  joint  NER  and  classification  are  discussed  in  the related work section.
  Afterwards,   pre-trained   language   models   on   large  corpus  like  BERT
  \cite{devlin2018bert}  and  RoBERTa \cite{liu2019roberta} has been proven more
  powerful  in  solving  many  NLP  tasks  including  short-text  classification
  \cite{madabushi2020cost}.      Especially      for      few-shot     scenarios
  \cite{yu2018diverse},     pre-trained     model    based    on    transformers
  \cite{vaswani2017attention} tends to do more
  help to reducing the negative effects brought by scarcity of training data.

  The  second  one,  \emph{similarity model} is also called sentence-pair model.
  Its  motivation  originates  from  the idea of Information Retrieval (IR) based
  chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Having   a  Q-A
  (Question-Answer)  pairs dataset and user query Q, the IR based conversational
  system will look up in the Q-A dataset for the pair (Q', A') that best matches
  query  Q  through  semantic  analysis  and  returns  A'  as  the  answer  to Q
  \cite{mnasri2019recent}. In this way, sentence-pair model pre-trained on large
  corpus  of  semantic  similarity  identification task can be applied for being
  used  as  a  tool  to  identify  the class with highest semantic similarity to
  customer's    query.    A    common    model    structure    of    pre-trained 
  sentence-pair model is based on multiple cross-attention
  mechanism  \cite{barkan2020scalable}. Due to
  the   fact   that   many   experiment   results   have   shown   that  RoBERTa
  \cite{liu2019roberta} is an improved version of BERT \cite{devlin2018bert}, and has achieved amazing
  results  on  both  text  classification and sentence-pairs semantic similarity
  tasks, we choose RoBERTa as an important baseline approach in this paper.

  Despite  the  success  of  these two kinds of approaches, they still have some
  limitations   in   task-specific  chatbot  scenario.  As  for  the  \emph{text
  classification  model},  it  is  quite hard to use data augmentation method to
  solve  the  data insufficiency challenge since the it is usually unfeasible to
  get  large amount of domain-specific data when facing a new task. With respect
  to  the  \emph{similarity model}, though we can obtain a large amount of data
  from semantically  duplicate  sentence  pair identification domain for transfer
  learning  \cite{sun2019fine},  it  is  still  quite  hard  to  perform well on
  a new task-specific dataset,  since their objective losses are totally different.

  The  above limitation motivates us to propose a joint system that is capable of
  taking  advantages  from  both  classification model and similarity model. We
  call  it  SFC,  short  for  similairty model fused with classification Model,
  shown  in  Fig.  \ref{fig:framework}.  To  better train SFC, we further bring in
  multi-task   learning   \cite{caruana1993multitask,collobert2008unified, liu2019multi}.  Our
  basic  idea  came  from  two  stages. In the first stage, we use an auxiliary
  model  to  select top-K most possible labels for a input. This model can be an
  elastic search  \cite{divya2013elasticsearch}  or  a  text classification model
  trained on current task-specific chatbot data. In the second stage, we build a
  classification  model  whose  main modules are similarity models. Then, this
  structure  derives two goals to train towards, the classification loss for our
  application,  and the similarity loss for the main modules. When the two stages
  are  independently  optimized,  we call \emph{two-stage SFC}. We further find,
  the  the  quality  of  output  from  the  first  stage  might  limit the final
  performance  of  system,  since  the  candidate  labels for each user query is
  always  fixed  in  the  whole  multi-task  training  process. This observation
  motivates  us  to  further  improve  the  two-stage SFC into a joint training,
  called  \emph{joint  SFC}. In this way, the sentence pairs associated with the
  top-K  classes  also  become dynamic, and the text classification model in the
  first  stage  will also be further optimized to provide better top-K result by
  the final training loss.

  We summarize our contributions as follow:
  \begin{enumerate}
    \item We propose a novel joint system to makes full utilization of
    the advantages from both text classification model and similarity model.

    \item To  better  train such a system, we bring in multi-task training to obtain
    reasonable performance.

    \item Experiment  results  from 4 public and 1 private short-text classification
    datasets,  show  that  our  proposed  SFC joint system can achieve significant
    and consistent improvements over strong baselines, especially in the low resource settings.
  \end{enumerate}

  \begin{figure*}[t]
    \begin{centering}
      \includegraphics[scale=0.72]{picture/picture4} 
      \par
    \end{centering}
    \caption{
      \textbf{Network Structure of SFC:} two-stage SFC and joint-SFC are sharing
      the  same  network  from  stage  1  and  stage 2, with the only difference
      whether two stages being jointly trained.
    }
    \label{fig:framework}
  \end{figure*}

  \section{Related work}

  Another  common  approach  is  text  classification  neural  network  based on
  label-word     joint     embedding,    such    as    LEAM \cite{wang2018joint},
  MTLE \cite{zhang2017multi}   and   EXAM \cite{du2019explicit}.   This   approach
  involves  label  embedding when constructing the text-sequence representation.
  Take  LEAM  as  an  example,  the  text classification model is implemented by
  jointly    embedding    the    word    and    label   in   the   same   latent
  space \cite{wang2018joint}. Afterwards, the text representation are constructed
  based  on  text-label  compatibility through attention mechanism. In this way,
  additional  sources  of  semantic  information  from class labels can be fully
  leveraged, which is quite helpful especially under few-shot scenario.

  As for \emph{label-word joint
  embedding  approach},  it  poses  noticeable requirements on label information.
  However,  in  our  cases,  since  we have large amount of class labels without
  being well-defined for question answering chatbot, the only thing we can do is
  to  choose  one  of the user utterance as the class label to represent the key
  information  of  the  whole class. In this way, the label will become not only
  prolix  but  also  biased,  which  will  bring  some  negative effect to label
  embedding.

  Another   line   of  interesting  work  is  the  joint  training  of  sentence
  classification   and  NER  (todo:  reference).  If  both  the  city  and  date
  information  are  recognized,  then  they  are good indicators that this query
  might  be  booking  an  ticket. This work can also be combined in our proposed
  framework.

  \section{Methodology}
  In  this section, we describe our proposed system, a similarity model fused with
  a classification  model (SFC). We propose two approaches to implement this idea,
  two-stage SFC, and its more compact version joint SFC.

  \subsection{Two-stage SFC}

  Two-stage   SFC  is  composed  with  two  independent stages  in  charge of
  different  jobs.

  \subsubsection*{
    Stage 1: classification model for providing top-K candidate class labels
  } 
  We  can  use any auxiliary text classification model or tool,
  such as Term Frequency-Inverse Document Frequency (TF-IDF)retrieval, to
  provide  top-K  most  related  class  labels. These selected class labels will
  later  be  used to sample sentence pairs of both positive samples and negative
  samples  for  stage  2.

  In  this  work,  we  choose pretrained models to fine tune on our data.
  Due to the excellent performance of RoBERTa in this task, compared to other pretrained
  models, we use RoBERTa as the encoder of classification model in our setting.

  Given   a   data   point   $x_{i}$  with  class  label  $y_{i}$  from  dataset
  $\mathcal{D}$, we take the final hidden state $h_{i}$ of the first token [CLS]
  encoded  by  RoBERTa  as the representation for the whole sequence of $x_{i}$.
  Then  a linear layer is followed to output probabilistic distribution of class
  labels,  $softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$,  where $W^C$ and $b^C$
  are  trainable  parameters.  Then, the loss in stage 1 classification model is
  shown in Equ. \ref{eq:classification_loss},

  \begin{equation}
    \begin{aligned}
      \mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\
      \label{eq:classification_loss}
    \end{aligned}
  \end{equation}

  \subsubsection*{
    Stage 2: sentence-pair similarity model based classification with multi-task
    learning
  }
  We  continue choosing RoBERTa as the main module in this stage that identifies
  the class label with strongest semantic similarity to the user input sentence.

  Suppose  we have a training dataset $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$ of
  $N$  data  points,  in  which $x_{i}$ is the user input query and $y_{i}$ is a
  single  class label from a class label set of $C$ classes in total. We 
  generate            a sentence            pair            dataset
  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$ from $\mathcal{D}$,   where   $(x,   x')_{j}$  is
  a pair of two history queries \footnote{For simplicity, we use query
  to denote a user's question or a response.}, and $l_{j}\in\{0, 1\}$ denotes the
  similarity label that only the ones from the same class label are considered
  similar. The size of $\mathcal{D'}$  would be up to $O(N^2)$ if no any
  sampling strategy is used.  This is quite time-consuming  for the  training
  in stage 2 because $N$ can be several hundreds or thousands even under 
  few shot setting in task-specific chatbot scenario.

  Therefore,  we  adopt  the idea of adversarial negative sampling strategy from
  the  work  \cite{bamler2020extreme}.  The  key  idea is to train with negative
  samples  that  are hard to be distinguished from positive samples. Now suppose
  we  have  a  user  input query $x_{i}$ and top-K most related class labels set
  $\mathcal{C'}=\{c'_{1},  \dots,  c'_{K}\}$ provided by auxiliary model or tool
  in  stage  1, where $K$ is a hyperparameter to control candidate class number,
  we  apply  the  adversarial  negative sampling strategy into our sentence pair
  sampling process by the following two steps:

  The  first step is \emph{positive sentence pair sampling}. During the training
  process,  we  first make sure the ground truth class label $y_{i}$ for $x_{i}$
  is  within  the  candidate  class  label  set  $\mathcal{C'}$. If $y_{i}\notin
  \mathcal{C'}$,  we  manually  add  $y_{i}$  into  $\mathcal{C'}$  by replacing
  $c'_{K}$  with  $y_{i}$, since $c'_{K}$ is the least promising candidate label
  according  to  the  auxiliary  model  in stage 1. Afterwards, we will randomly
  sample  $P$ sentences $\{x'_{1}, \dots, x'_{P}\}$ with the same class label as
  $y_{i}$  from  dataset  $\mathcal{D}$  to  form the set of sentence pairs with
  positive  label  $\mathcal{P'}_{i}=\{[(x_{i},  x'_{1}),  1],  \dots,  [(x_{i},
  x'_{P}),  1]\}$,  where $P$ is also a hyperparameter set to control the number
  of sentences we should sample from each class.

  \begin{table*}
    \begin{centering}
      \scalebox{0.9}{
        \begin{tabular}{|c|c|c|c|c|c|}
          \hline 
          \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
          \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
          \hline 
          ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
          \hline 
          Amazon-670k & Product review & 250 & 1942 & 8 & 3-fold\tabularnewline
          \hline 
          HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
          \hline 
          CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
          \hline 
          BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
          \hline 
        \end{tabular}
      }
      \par
    \end{centering}
    \caption{Statistics for all datasets and few shot settings.}

    \label{tbe:dataset statistic}
  \end{table*}

  The  second  step  is  \emph{negative sentence pair sampling}: As for negative
  sentence  pairs,  we will also randomly sample $P$ sentences for each class in
  the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$. The
  class  labels  in  $\mathcal{C'}\backslash  \{y_{i}\}$  are  the  set  of most
  confusing  class  labels comparing to the ground truth ${y_{i}}$, so we assume
  that  the  sentence  pairs  with  negative  label  grouped by user input query
  $x_{i}$  and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$
  are  strong  adversarial  negative  samples for sentence-pair similarity model
  that  can  help  enhance  the training speed and performance. According to the
  same  method  as  positive  sentence  pair  sampling, we can obtain the set of
  sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{1}),
  0], ..., [(x_{i}, x'_{P\cdot K}), 0]\}$

  In  this way, we generate the sentence pair dataset $\mathcal{D'}$ for stage 2
  based  on  the  top-K  class  label  set $\mathcal{C'}$ provided by stage 1 as
  $\mathcal{D'}=\{\mathcal{P'}_{i}\cup  \mathcal{N'}_{i}\}_{i=1}^{N}$,  in which
  we have $M=N\cdot K\cdot P$ data points of sentence pairs in total.

  Before starting to fine-tune our sentence-pair model on task-specific dataset,
  we  first  fine-tune  RoBERTa  on  Quora  dataset  \cite{iyer2017first}, which
  contains  404,290  potential  duplicate question pairs, for transfer learning.
  This  is  also  the  merit of similarity based model, as labeled task-specific
  classification  data  is  hard  to  acquire,  yet  general sentence pairs with
  similar semantics can be much easier to acquire.

  \subsubsection*{Multi-task based training}
  We   continue  to  do  multi-task  training  on  sentence-pair  dataset
  $\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage
  1. In stage 2, we have two tasks tuning our system.

  The first task is \emph{regular sentence-pair similarity task}.
  For  sentence  pair semantic similarity task, given a data point $(x, x')_{i}$
  with       similarity       label       $l_{i}$       from       data      set
  $\mathcal{D'}=\{[(x,x')_{i},l_{i}]\}_{i=1}^{M}$,   Roberta   takes  the  final
  hidden  state  $h_{i}$  of the first token [CLS] as the representation for the
  sequence of packed sentence pair $(x, x')_{i}$. Let's suppose we have a linear
  layer  as  ${\Phi}^S_{i}=W^Sh_{i}+b^S$,  where  $W^S$  and $b^S$ are trainable
  parameters,  and  the probability score for $(x, x')_{i}$ can be calculated as
  $p^S_{i}=softmax({\Phi}^S_{i})$.

  Due  to  the  fact that sentence pairs within the same class is much fewer than
  that from  different  classes,  the  dataset  $\mathcal{D'}$  is
  quite imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
  to  the  loss  to eliminate the bias brought by data imbalance, shown in Equ.
  \ref{eq:similarity_loss}.

  \begin{equation}
    \begin{aligned}
      \mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\
      \label{eq:similarity_loss}
    \end{aligned}
  \end{equation}

  The  second  task  is  \emph{classification  on  top-K classes}. As minimizing
  similarity  loss  is  not  our  final goal in the intention classification, we
  bring  back  classification  loss again. In this task, the network is based on
  sentence  pair  similarity  modules.  The  only  difference  is  that we add a
  task-specific  average  pooling  layer,  shown  in Fig. \ref{fig:framework} to
  accomplish the classification task based on sentence-pair model.

  We  already  know  that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot
  K\cdot  P)\times  2$, where $N$ is the total number of data points in original
  training  data $\mathcal{D}$, $K$ is a hyperparameter that controls the number
  of   candidate   class  labels  provided  by  stage  1,  and  $P$  is  also  a
  hyperparameter that controls the number of sentences we should randomly sample
  from each candidate class labels. Now, for the average pooling layer, we first
  reshape  ${\Phi}^S$  into  the  size  of $N\times K\times P\times 2$, and then
  split  it  into  ${\Phi}^{K,pos}$  and ${\Phi}^{K,neg}$, and both of them will
  have  the  size  of  $N\times  K\times  P$.  In this way, ${\Phi}^{K,pos}$ can
  represent  the  level  of  similarity  for each sentence pair, and in the mean
  time,  ${\Phi}^{K,neg}$  can  represent  the  level  of dissimilarity for each
  sentence  pair. Then, we can do average pooling for each candidate class among
  the  top-K  classes  as  shown  in  Equ.  \ref{eq:average  pooling}.

  \begin{align}
    {\xi}_{i,j}^{K,pos} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,pos} \ \ \ \ \ \ \ 
    {\xi}_{i,j}^{K,neg} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,neg}
    \label{eq:average pooling}
  \end{align}

  With  the  average pooling result ${\xi}^{K,pos}$ and ${\xi}^{K,neg}$, we also
  generate   a   top-K   class   label   $l^{K}_i\in   [1,\dots,K]$   for   each
  ${\xi}^{K,pos}_{i}$ and ${\xi}^{K,neg}_{i}$. The loss for top-K classification
  task is shown in Equ. \ref{eq:top-k_classification_loss}. In Equ. \ref{eq: pos
  top-k   loss}   and   Equ.   \ref{eq:   neg   top-k   loss},  the  first  term
  $\xi_{i,l^{K}_{i}}^{K,pos}$  and  $\xi_{i,l^{K}_{i}}^{K,neg}$  encourage  high
  level  of  similarity  and  low  level  of dissimilarity for prediction of the
  correct label $l^{K}_i$ within the top-K candidate classes.

  \begin{align}
    \mathcal{L}^{K} = \frac{1}{N}\sum_{i=1}^{N}(\mathcal{L}^{K,pos}_{i} - \mathcal{L}^{K,neg}_{i})
    \label{eq:top-k_classification_loss}
  \end{align}
  where

  \begin{equation}
    \begin{aligned}
      \mathcal{L}^{K,pos}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,pos})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos})})
      \label{eq: pos top-k loss}
    \end{aligned}
  \end{equation}

  \begin{equation}
    \begin{aligned}
      \mathcal{L}^{K,neg}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,neg})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg})}) \\
      \label{eq: neg top-k loss}
    \end{aligned}
  \end{equation}

  Finally,  the  overall  loss  function for multi-task learning in stage 2 is
  shown in Equ. \ref{eq:two-stage_SFC_loss}. The training objective of stage 2 is
  to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively.

  \begin{align}
    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
    \label{eq:two-stage_SFC_loss}
  \end{align}

  \begin{table*}
    \begin{centering}
      \scalebox{0.55}{
        \begin{tabular}{|c|cccccc|cccccc|cccccc|c|c|}
          \hline 
          \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{6}{c|}{\textbf{CLINC150}}& \multicolumn{6}{c|}{\textbf{BANKING77}}& \multicolumn{6}{c|}{\textbf{HWU64}}& \ \ \ \textbf{ITG} \ \ \ & \textbf{Amazon-670k}\tabularnewline
          \cline{2-21}
          \multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$
          & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ &
          $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ &
          $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ &
          $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & \textbf{3-fold} &
          \textbf{3-fold}\tabularnewline
          \hline
          TextCNN & \multirow{2}*{$0.5318$} & \multirow{2}*{$0.6963$} & \multirow{2}*{$0.7609$} & \multirow{2}*{$0.8142$} & \multirow{2}*{$0.8526$} & \multirow{2}*{$0.8867$} & \multirow{2}*{$0.4408$} & \multirow{2}*{$0.6436$} & \multirow{2}*{$0.7366$} & \multirow{2}*{$0.7918$} & \multirow{2}*{$0.8228$} & \multirow{2}*{$0.8619$} & \multirow{2}*{$0.3112$} & \multirow{2}*{$0.4007$} & \multirow{2}*{$0.4823$} & \multirow{2}*{$0.5272$} & \multirow{2}*{$0.5782$} & \multirow{2}*{$0.6262$} & \multirow{2}*{$0.6624$} & \multirow{2}*{$0.4401$}\tabularnewline
          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
          LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.8802$} & \multirow{2}*{$0.9010$} & \multirow{2}*{$0.9180$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.8610$} & \multirow{2}*{$0.8727$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.6855$} & \multirow{2}*{$0.7046$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
          \hline
          BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.9334$} & \multirow{2}*{$0.9497$} & \multirow{2}*{$0.9595$} & \multirow{2}*{$0.5780$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.8858$} & \multirow{2}*{$0.8982$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7117$} & \multirow{2}*{$0.7424$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
          ALBERT-xxlarge & \multirow{2}*{$0.8497$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.9297$} & \multirow{2}*{$0.9466$} & \multirow{2}*{$0.9578$} & \multirow{2}*{$0.5549$} & \multirow{2}*{$0.7981$} & \multirow{2}*{$0.8231$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.8571$} & \multirow{2}*{$0.9096$} & \multirow{2}*{$0.4879$} & \multirow{2}*{$0.6116$} & \multirow{2}*{$0.6135$} & \multirow{2}*{$0.6996$} & \multirow{2}*{$0.7094$} & \multirow{2}*{$0.7376$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
          RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.9482$} & \multirow{2}*{$0.9558$} & \multirow{2}*{$0.9637$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.9061$} & \multirow{2}*{$0.9293$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7320$} & \multirow{2}*{$0.7472$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
          RoBERTa-large & \multirow{2}*{$\textbf{0.8974}$} &
          \multirow{2}*{$\textbf{0.9372}$} & \multirow{2}*{$\textbf{0.9508}$} &
          \multirow{2}*{$\textbf{0.9584}$} & \multirow{2}*{$\textbf{0.9621}$} & 
          \multirow{2}*{$\textbf{0.9733}$} & \multirow{2}*{$\textbf{0.7690}$} & 
          \multirow{2}*{$\textbf{0.8728}$} & \multirow{2}*{$\textbf{0.8966}$} & 
          \multirow{2}*{$\textbf{0.9099}$} & \multirow{2}*{$\textbf{0.9227}$} & 
          \multirow{2}*{$\textbf{0.9313}$} & \multirow{2}*{$\textbf{0.6044}$} & 
          \multirow{2}*{$\textbf{0.7002}$} & \multirow{2}*{$\textbf{0.7129}$} & 
          \multirow{2}*{$\textbf{0.7436}$} & \multirow{2}*{$\textbf{0.7493}$} & 
          \multirow{2}*{$\textbf{0.7678}$} & \multirow{2}*{$\textbf{0.7990}$} & 
          \multirow{2}*{$\textbf{0.7156}$}\tabularnewline
          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
          \hline
          RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.9084$} & \multirow{2}*{$0.9090$} & \multirow{2}*{$0.9407$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.8749$} & \multirow{2}*{$0.8980$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.6947$} & \multirow{2}*{$0.7231$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
          (similarity) & & & & & & & & & & & & & & & & & & & &\tabularnewline
          \hline
          2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.9591$} & \multirow{2}*{$0.9610$} & \multirow{2}*{$0.9664$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.9187$} & \multirow{2}*{$0.9198$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7484$} & \multirow{2}*{$0.7653$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
          (task1) & & & & & & & & & & & & & & & & & & & &\tabularnewline
          2-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.9617$} & \multirow{2}*{$0.9633$} & \multirow{2}*{$0.9690$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.9236$} & \multirow{2}*{$0.9317$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.7498$} & \multirow{2}*{$0.7657$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
          (task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
          2-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.9638$} & \multirow{2}*{$0.9658$} & \multirow{2}*{$0.9753$} & \multirow{2}*{$0.8135$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.9257$} & \multirow{2}*{$0.9339$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7092$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$0.7519$} & \multirow{2}*{$0.7696$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
          (task1 + task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
          \hline
          \multirow{2}*{Joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
          & & & & & & & & & & & & & & & & & & & &\tabularnewline
          \hline
        \end{tabular}
      }
      \par
    \end{centering}
    \caption{
      F1 scores  on  five  task-specific  datasets text classification in chatbot
      under low resource. For ITG, we keep the full dataset. For Amazon-670k, we
      randomly  sampled  250  classes  with  training sample numbers within 5-15

>>>>

  \input{abstract}
  \input{introduction}
  \input{related_work}
  \input{methodology}
  \input{experiments}
  \input{conclusion}
